Engaging in any cheating or dishonesty in any form of assessment, 
assignment, test orexamination or other WeThinkCode\_ prescribed work 
is considered cheating and is grounds for disciplinary action.
Plagiarism, which is to present work (or a portion of work) as your 
own when it is not, isconsidered cheating and is not accepted at 
WeThinkCode\_.

An evaluator can flag one for plagiarism on one of the following grounds\
:\begin{itemize}
     
\item The evaluator (marker) identifies that the student does not understand
all or part of the work they have submitted.
\item If all or part of the work presented is plagiarised ,i.e. copied from 
another source without reference.
\end{itemize}

\begin{large}\textbf{Cheating in group projects}\end{large}\\

The main purpose for a group project is to give students the experience of working in ateam, by coming up with a solution to a problem together.
\begin{itemize}
    \item Each member must be able to show which portion of the project they worked on. 
    \item Failure to do so will result in the student being flagged for cheating which will begrounds for disciplinary action.
    \item This is to avoid single members doing the majority of the group project at the benefit of a member who is not contributing.
    \item In this way we are able to ensure fair assessment of each WTC\_ student’s competence.
\end{itemize}    
Group projects can be approached in two ways.
\begin{enumerate}
    \item Divide and conquer: This is usually preferred and advised when working on big projects. The project is divided into segments, in which each member of the group can accomplish. Once completed, the group will then integrate the segments to complete the project
    \item One for all: This method is usually preferred and advised when a group is working on a small project. The group will work on the solution together from the start of the project until the end. This will require the members to move at a pace in which everyone in the team can keep up with.
\end{enumerate}    
NOTE: At the end of each group project, each member should have a general and basic understanding of the project and the solution found. This will include running,testing and explaining the solutions of the project.

\section*{Declaration}

I hereby declare that the work submitted by me and/or my group members is:
\begin{itemize}
    \item Original (not plagiarised)
    \item References listed
    \item Honest \& in Good Faith
    \item Subject to WeThinkCode\_policies
\end{itemize}

\vspace{15mm}

\begin{minipage}{0.4\textwidth}
    \begin{flushleft}
        \large
        \line(1,0){120}\\
        Mosima \textsc{Mamaleka} % Your name
        \textit{WeThinkCode\_ Student}\\
    \end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
    \begin{flushright}
        \large
        \line(1,0){120}\\
        Sibonelo \textsc{Nkosi} % Supervisor's name
        \textit{WeThinkCode\_ Student}\\
    \end{flushright}
\end{minipage}

% \begin{flushleft}
% \line(1,0){120}\\
% Sibonelo \textsc{Nkosi}\\ % Your name
% Username: \textsc{sinkosi}\\ % Your name
% {\large\textit{Developer}}
% \end{flushleft}